Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex
Update paper.tex

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8cm]{320.pdf}
\caption{Visual representation of how the User File System reads and writes files from and to Dropbox.}
\label{fig:userfilesys}
\end{center}
\end{figure}

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of $Z$ = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput as the performance metric, which is a measurement of how fast files can be read from and written to our ORAM-enabled Dropbox. It is expressed in bits per second or multiples of it. For our experiments we use megabytes per second (MB/s).

@@

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function showing the cumulative percentage of files of various sizes (KB).}
\label{fig:distfun}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{320.pdf}
\caption{Visual representation of how the User File System splits and then reads/writes files from/to Dropbox.}
\label{fig:userfilesys}
\end{center}
\end{figure}

@@

@@

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of $Z$ = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput in Mega Byte per second as the performance metric.
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function showing the cumulative percentage of files of various sizes (KB).}
\label{fig:distfun}
\end{center}
\end{figure}
